Named Entity Recognition as Structured Prediction

### 2012-11-11 doc/report/paper.tex
+++

\documentclass[11pt]{article}
\usepackage{acl2011}
\usepackage[utf8]{inputenc}
\usepackage{linguex}
\usepackage{latexsym}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{array}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{qtree}
\usepackage{textcomp}
\usepackage{todonotes}

@@

In the following, we show the influence of each of the three sets of features on the resulting accuracy.

%INSERT MATLAB PIC HERE

@@

This paper presented a system for \namedentity Recognition using Structured Prediction.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2011}
\usepackage[utf8]{inputenc}
\usepackage{linguex}
\usepackage{latexsym}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{array}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{qtree}
\usepackage{textcomp}
\usepackage{todonotes}
\usepackage{placeins}

@@

In the following, we show the influence of each of the three sets of features on the resulting accuracy.
\FloatBarrier
\begin{figure*}[t!]
 \includegraphics[scale=0.5]{Plot.png}
\end{figure*}

@@

In this paper, we presented a \namedentity~Recognition system based on the concept of Structured Prediction. 
While the system does not achieve state-of-the-art performance on the CoNLL shared task, we believe that the results 
are reasonable for the following reasons. We are using a simple model, which has the advantage that the final application 
will be fast and it is easily extendable. In contrast to the best systems in the CoNLL task, we also do not use ensemble 
learning methods and we use the same set of features for all languages, which enables simple extension of the system to additional languages.
